Optimizing Path ORAM for Cloud Storage Applications

### 2014-11-30 paper/paper.tex
title and email
made Figure 8 bigger

\title{Protecting Private Data in the Cloud: A Path Oblivious RAM Protocol}

@@

\author{\IEEEauthorblockN{Nathan Wolfe}
\IEEEauthorblockA{The Roxbury Latin School\\ 
Email: nathanwolferl@gmail.com}
\and
\IEEEauthorblockN{Ethan Zou}
\IEEEauthorblockA{Lexington High School\\ 
Email: zouethan19@gmail.com}
\and
\IEEEauthorblockN{Ling Ren}
\IEEEauthorblockA{MIT}
\and
\IEEEauthorblockN{Xiangyao Yu}
\IEEEauthorblockA{MIT}
}

@@

\label{sec:BlkPack}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=4cm]{550.pdf}\includegraphics[width=4cm]{551.pdf}
\caption{Block Packing Evaluations}
\label{fig:blockpack}
\end{center}
\end{figure}

>>>>

\title{Optimizing Path ORAM for Cloud Storage Applications}

@@

\author{\IEEEauthorblockN{Nathan Wolfe}
\IEEEauthorblockA{The Roxbury Latin School\\ 
Email: nathanwolferl@gmail.com}
\and
\IEEEauthorblockN{Ethan Zou}
\IEEEauthorblockA{Lexington High School\\ 
Email: zouethan19@gmail.com}
\and
\IEEEauthorblockN{Ling Ren}
\IEEEauthorblockA{MIT \\
Email: renling@mit.edu} \and
\IEEEauthorblockN{Xiangyao Yu}
\IEEEauthorblockA{MIT\\
Email: yxy@mit.edu}
}

@@

\label{sec:BlkPack}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=4.3cm]{550.pdf}\includegraphics[width=4.3cm]{551.pdf}
\caption{Block Packing Evaluations}
\label{fig:blockpack}
\end{center}
\end{figure}
